### 2017-09-27 TF-vldb2018/sec-appendix.tex

\revise{
We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
We know that $P\eps \ball{[v, t]}$, and $M_t$ is a match relation for $P$ in $\ball{[v, t]}$.
Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
there must exist a binary relation $M_r$ such that for any $(u, v) \in M_t$, where $u$ is a pattern node and $v$ is the matched data node of $u$ in $\ball{[v, t]}$, 
$(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
Since $M_t$ is a match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.

@@

\vspace{-1.5ex}
\begin{figure}[h!]
\label{fig-inc-complexity-data}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit data update}
\vspace{-2ex}
\end{figure}

@@

\vspace{-1ex}
\begin{figure}[h!]
\label{fig-inc-complexity-pattern}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-pattern.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit pattern update}
\vspace{-1.5ex}
\end{figure}

@@

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-extraspace}
\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
\vspace{-2ex}

@@

\vspace{-1.8ex}
\stitle{Exp-4: Physical storage of auxiliary structures}. It takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
\ie 50.8\% compared with the original dataset.

>>>>

\revise{
We will prove Theorem~\ref{thm-tsim-radius} (1) firstly.
We know that $P\eps \ball{[v, t]}$, and suppose that $M_t$ is a binary match relation for $P$ in $\ball{[v, t]}$.
Since $\ball{[v, t]}$ is a subgraph of $\ball{[v, r]}$, 
there must exist a binary relation $M_r$ such that for any $(u, v) \in M_t$, where $u$ is a pattern node and $v$ is the matched data node of $u$ in $\ball{[v, t]}$, 
$(u, v) \in M_r$ holds, where $v$ is the matched data node of $u$ in $\ball{[v, r]}$, \ie $M_t \subset M_r$.
Since $M_t$ is a match relation for $P$ in $\ball{[v, t]}$ and $M_t \subset M_r$, by the definition of graph simulation, then $P\eps \ball{[v, r]}$ and $M_r$ is a match relation for $P$ in $\ball{[v, r]}$.

@@

\vspace{-1.5ex}
\begin{figure}[ht!]
\label{fig-inc-complexity-data}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit data update}
\vspace{-4ex}
\end{figure}

@@

\vspace{-1ex}
\begin{figure}[ht!]
\label{fig-inc-complexity-pattern}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-pattern.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit pattern update}
\vspace{-4ex}
\end{figure}

@@

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi-youtube}
\includegraphics[scale=0.38]{./fig/youtube-pattern-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Storage sizes}]{\label{fig-exp-youtube-extraspace}
\includegraphics[scale=0.38]{./fig/youtube-space.eps}}
\vspace{-2ex}

@@

\vspace{-1.8ex}
\stitle{Exp-4: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-youtube-extraspace},
it takes 58MB extra space to store all auxiliary structures utilized by \inc on \youtube, which need 114MB space to store itself,
\ie 50.8\% compared with the original dataset.
